*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-13 Code/Manuscript_O2.Rmd
Copied .rmd from before I started changing the output destination. Still no equations in .docx

---
title: "*Prochlorococcus marinus* responses to light and oxygen" 
author:
  - name: 'Mireille Savoie'
    institute: mta
    main: true
    email: msavoie@mta.ca
  - name: Aurora Mattison
    institute: [mta, ubc]
  - name: Laurel Genge
    institute: [mta, dfo]
  - name: Julie Nadeau
    institute: mta
  - name: Sylwia Śliwińska-Wilczewska
    institute: [mta, ug]
  - name: Maximilian Berthold
    institute: mta
  - name: Naaman M. Omar
    institute: mta
  - name: Ondřej Prášil
    institute: [mta, algatech]
    main: false
  - name: Amanda M. Cockshutt
    institute: [mta, sfx]
    main: false
  - name: Douglas A. Campbell
    institute: mta
    affil: 1
    orcid: '0000-0001-8996-5463'
    email: 'dcampbel@mta.ca'
    correspondence: true
affiliation:
  - num: 1
    address: Departments of Biology and Chemistry and Biochemistry, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 63B York St., Sackville NB, Canada, E4L 1G7'
  - ubc: 'Department of Biology, University of British Columbia'
  - dfo: 'Fisheries and Oceans Canada, Ecosystems Management Branch, Dartmouth NS'
  - sfx: 'Department of Chemistry, St. Frances Xavier University'
  - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Novohradska 237, Trebon, CZ 37981, Czech Republic.'
  - ug: 'Institute of Oceanography, University of Gdansk, 46 Piłsudskiego St, Gdynia, Poland'
date: "`r format(Sys.Date())`"
output:
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: FALSE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: ["`r file.path('..', 'Docs', 'Manuscript_O2.bib')`", "`r file.path('..', 'Docs', 'RPackages.bib')`", "`r file.path('..', 'Docs', 'FaultyCitations.bib')`"]
csl: "`r file.path('..', 'Docs', 'plos-one.csl')`"
editor_options: 
  markdown: 
    wrap: 72
knit: (function(input, encoding) {
  rmarkdown::render(input,
                    output_dir = file.path('..', 'Output'))})
---

@@

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')

@@

knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm"), file.path("..", "Docs",'RPackages.bib'))

```{r set project variables, include = FALSE}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "CleanData")
FiguresIn <- file.path("..","Output", "Figures")

>>>>

---
title: "*Prochlorococcus marinus* responses to light and oxygen" 
author:
  - name: 'Mireille Savoie'
    institute: mta
    main: true
    email: msavoie@mta.ca
  - name: Aurora Mattison
    institute: [mta, ubc]
  - name: Laurel Genge
    institute: [mta, dfo]
  - name: Julie Nadeau
    institute: mta
  - name: Sylwia Śliwińska-Wilczewska
    institute: [mta, ug]
  - name: Maximilian Berthold
    institute: mta
  - name: Naaman M. Omar
    institute: mta
  - name: Ondřej Prášil
    institute: [mta, algatech]
    main: false
  - name: Amanda M. Cockshutt
    institute: [mta, sfx]
    main: false
  - name: Douglas A. Campbell
    institute: mta
    affil: 1
    main: false
    orcid: '0000-0001-8996-5463'
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Departments of Biology and Chemistry and Biochemistry, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 63B York St., Sackville NB, Canada, E4L 1G7'
  - ubc: 'Department of Biology, University of British Columbia'
  - dfo: 'Fisheries and Oceans Canada, Ecosystems Management Branch, Dartmouth NS'
  - sfx: 'Department of Chemistry, St. Frances Xavier University'
  - algatech: 'Institute of Microbiology, Center Algatech, Laboratory of Photosynthesis, Novohradska 237, Trebon, CZ 37981, Czech Republic.'
  - ug: 'Institute of Oceanography, University of Gdansk, 46 Piłsudskiego St, Gdynia, Poland'
date: "`r format(Sys.Date())`"
output:
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: FALSE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Manuscript_O2.bib, RPackages.bib, FaultyCitations.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

knitr::write_bib(c("knitr", "tidyverse", "lubridate", "ggplot2", "broom", "grid", "bookdown", "glue", "cowplot", "ggpubr", "ggh4x", "png", "zoo", "photobiology", "photobiologyWavebands", "data.table", "googlesheets4",  "mgcv", "minpack.lm"), 'RPackages.bib')

@@

```{r set project variables, include = FALSE}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "CleanData")
FiguresIn <- file.path("..","Output", "Figures")
FigureInO2Analy <- file.path(  "..", "..", "O2Analyses", "Output")
